\textit{Supplementary materials for}: Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-25 paper/supplement.tex
cleaned up supplement

\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
text embeddings of each question about \textit{Four Fundamental Forces} (FFF)
and \textit{Birth of Stars} to identify corresponding matching intervals of the
lectures. The text of the questions and the best-matching time intervals of the
lecture transcripts are displayed (lecture times are noted in square brackets).
Time courses of topic correlations for each question may be found in
Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
no matching lecture interval was found for Question 29.} 
\label{tab:matches}
\end{longtable}
\end{tiny}

>>>>

\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
text embeddings for each question about \textit{Four Fundamental Forces} (FFF)
and \textit{Birth of Stars} (BoS) to identify corresponding matching intervals of the
lectures. The text of the questions and the best-matching time intervals of the
lecture transcripts are displayed (lecture times are noted in square brackets).
Time courses of topic correlations for each question may be found in
Supplementary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
no matching lecture interval was found for Question 29.} 
\label{tab:matches}
\end{longtable}
\end{tiny}
